Fivebranes

### 2022-03-15 fivebranes/index.tex
cleaning

\begin{document}
\section{Supersymmetric indices}

\subsection{A single fivebrane}

We recall the description of the holomorphic twist of a single fivebrane theory \cite{SWtensor}

@@

The holomorphic twist of the fivebrane theory is defined on any complex three-fold $X$ (which is not necessarily Calabi--Yau).
To define the theory we must assume that $X$ is equipped with a square-root of the canonical bundle $K_X^{1/2}$.

The theory is $\Z \times \Z/2$ graded but in this section we only need to recall its totalization as a $\Z/2$ graded theory. 
There are four fundamental fields $(\mu, \Omega, \phi_1,\phi_2)$ which consist of even Dolbeault forms of type $(2,1)$ and $(3,0)$ on $X$:
\[
\mu \in \Omega^{2,1}(X), \quad \Omega \in \Omega^{3,0}(X),
\]
and a pair of even sections:
\[
(\phi_1,\phi_2) \in \Omega^0(X , K^{1/2}_X) \otimes \C^2 .
\]
%where $R \cong \CC^2$ is the fundamental $Sp(1)$ representation. 
The equations of motion read
\beqn
\label{eqn:eom}
\begin{split}
\del \mu + \dbar \Omega & = 0 \\
\dbar \mu = \dbar \phi = \dbar \psi & = 0 .
\end{split}
\eeqn

There are gauge symmetries for the fields $\mu, \Omega$ determined by a ghost $b$ which is a Dolbeault form of type $(2,0)$ which acts simply by
\beqn
\label{eqn:ghost}
\begin{split}
\mu & \mapsto \mu + \dbar b  \\
\Omega & \mapsto \Omega + \del b .
\end{split}
\eeqn

This theory does not admit a Lagrangian description. 
However, it can still be put in a degenerate form of the BV formalism where the space of fields above is equipped with an odd Poisson bivector \cite{SWtensor}.

We now consider the case $X = \C^3$ and consider the local operators of the single fivebrane theory supported at $0 \in \C^3$.

@@

@@

Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\beqn\label{eqn:special1}
q = r^2 , \quad t_2 = 1 .
\eeqn
As one can easily check, this specialization yields the following single particle index
\[
f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$.

\subsection{Character of $E(3|6)$}

@@

\subsection{Large $N$ Holomorphic Character}

>>>>

\begin{document}

\section{The representation theory of local operators}

operators, indices, etc..
relationship to the $S^5$ partition function.

\subsection{Local operators in a holomorphic theory}

@@

Suppose that $V$ is a translation invariant holomorphic vector bundle on $\C^n$ equipped with a $\Z \times \Z/2$ bigrading. 
Let $\cV$ denote its sheaf of holomorphic sections.
The {\em space of fields} of a holomorphic field theory on $\C^n$ is the $\Z \times \Z/2$ graded complex of vector bundles
\[
\Omega^{0,\bu}(\C^n, V) \cong \Omega^{0,\bu}(\C^n) \otimes V_0 
\]
where $V_0$ is the fiber of $V$ at $0 \in \C^n$.
Our grading conventions are so that $\d \zbar_i$ has bidegree $(1,0)$.

As introduced in \cite{BWhol,LiVertex,CG2}, a {\em holomorphic field theory} is a holomorphic vector bundle $V$ as above equipped additionally with:
\begin{itemize}
\item The structure of a local (super) $L_\infty$ algebra on $V[-1]$ with structure maps given by holomorphic polydifferential operators
\[
[\cdot]_k \colon \cV[-1]^{\times k} \to \cV[1-k] .
\]
\end{itemize}
A {\em free} holomorphic theory has $[\cdot]_k = 0$ for $k > 1$.

\parsec[s:localops]

\begin{eg}
Suppose that $V$ is the trivial bundle on $\C^n$. 
Then, the space of local operators is the symmetric algebra on the topological vector space which is linear dual to 
\[
\cO^{hol}(\Hat{D}^n) = \C[[z_1,\ldots,z_n]] .
\]
Via the $n$-dimensional residue one can identify the algebra of local operators with 
\[
\Sym\left(\frac{\d z_1}{z_1} \cdots \frac{\d z_n}{z_n}  \C[z_1^{-1}, \ldots , z_n^{-1}]\right) .
\]

Consider the standard torus action $\C^\times \times \cdots \C^\times$ on $\C^n$. 
The equivariant character of local operators with respect to this symmetry is given by the plethystic exponential of the following `single particle index'
\[
\frac{1}{(1-q_1)\cdots (1-q_n)} .
\]
\end{eg}

\subsection{Operators on a single fivebrane}

We recalled the description of the holomorphic twist of the theory on a single fivebrane in \ref{s:single}. 
This theory exists on any complex three-fold $X$. 
To describe the algebra of local operators we specialize to $X = \C^3$ and consider the local operators supported at $0 \in \C^3$.

The theory on a single fivebrane is free and the underlying cochain complex of fields on $\C^3$ is given by 
\beqn
\begin{tikzcd}
\ul{-1} & \ul{0} \\
\Omega^{2,\bu}(\C^3) \ar[r,"\del"] & \Omega^{3,\bu}(\C^3) \\
\Pi \Omega^{0,\bu}(\C^3, K_{\C^3}^{1/2} \otimes \C^2) . 
\end{tikzcd} 
\eeqn
Here we recall the $\Z \times \Z/2$ bigrading where the differential has bidegree $(1,0)$.

@@

\brian{i think I will recall some of this in the language of `fields' in Section 1, but it'd be good to say a few words about operators.}

@@

Both deformations break the global Cartan subgroup down to $U(1) \times U(1)$ according to the specializations
\beqn\label{eqn:special1}
q = r^2 , \quad t_2 = 1 .
\eeqn
As one can easily check, this specialization yields the following single particle index
\[
f_{tensor}(t_1, 1, q, q^{1/2}) = \frac{q}{1-q} 
\]
which recovers the single particle index of a single chiral boson on the Riemann surface $\Sigma = \C_{z_1}$. 
Notice that although the Cartan subalgebra generated by the vector field $z_1 \del_{z_1} - z_2 \del_{z_2}$ is unbroken by this deformation, the dependence on its fugacity $t_1$ completely drops out of the expression.

\subsection{A stack of two fivebranes}

@@

\subsection{The large $N$ limit}
